Experiment 1a: Analysis of Root Questions, Context

### 2023-01-30 analysis/03_experiment/rscripts/main_analysis.Rmd
analysis 03 exp

# set the color palette for color-blind
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")

@@

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d$ModalPresent = as.factor(d$ModalPresent)
d$Wh = as.factor(d$Wh)
d$paraphrase = as.factor(d$paraphrase)
contrasts(d$paraphrase)
```

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d.ms.ma = d %>%
  filter(paraphrase %in% c("a","every")) %>%
  # hand-code paraphrase so mean-centering is more interpretatble 
  # (otherwise, "every" will be 1 and "a" will be 0 by default)
  mutate(paraphrase.dc = recode(paraphrase, "a" = 1, "every" = 0) ) %>%
  # mean-center
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))
```

>>>>

# set the color palette for color-blind
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999")

@@

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d$ModalPresent = as.factor(d$ModalPresent)
d$Wh = as.factor(d$Wh)
d$paraphrase = as.factor(d$paraphrase)
contrasts(d$paraphrase)
#       every the
# a         0   0
# every     1   0
# the       0   1

contrasts(d$Wh)
#       what when where who why
# how      0    0     0   0   0
# what     1    0     0   0   0
# when     0    1     0   0   0
# where    0    0     1   0   0
# who      0    0     0   1   0
# why      0    0     0   0   1
```

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d.ms.ma = d %>%
  filter(paraphrase %in% c("a","every")) %>%
  # hand-code paraphrase so mean-centering is more interpretatble 
  # (otherwise, "every" will be 1 and "a" will be 0 by default)
  mutate(paraphrase.dc = recode(paraphrase, "a" = 1, "every" = 0) ) %>%
  # mean-center
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms.ma$Wh) = cbind("how.vs.when"=c(1,0,0,0,0,0),
                              "what.vs.when"=c(0,1,0,0,0,0),
                              "where.vs.when"=c(0,0,0,1,0,0),
                              "who.vs.when"=c(0,0,0,0,1,0),
                              "why.vs.when"=c(0,0,0,0,0,1))
contrasts(d.ms.ma$Wh)

#       how.vs.when what.vs.when where.vs.when who.vs.when why.vs.when
# how             1            0             0           0           0
# what            0            1             0           0           0
# when            0            0             0           0           0
# where           0            0             1           0           0
# who             0            0             0           1           0
# why             0            0             0           0           1
```
